What is confining the proplyd bow shocks in Orion?

### 2017-01-26 papers/Paper1/quadrics-appendix.tex
Finish derivation of Rc in thin shell model. Derivation of R90 unfinished

\section{Analytic derivation of the raius of curvature in the Thin Shell model}
\label{app:rc-r90-analytic}

@@

\begin{align}
\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
\left(1-\frac{\beta}{15}\theta^2\right) \\
\implies \theta_1^2 &= \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right]\\
\mathrm{where:~} A_k &\equiv \frac{1}{15}-\frac{3k}{20}
\end{align}

>>>>

\section{Analytic derivation of the radius of curvature in the Thin Shell model}
\label{app:rc-analytic}

@@

\begin{align}
\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
\left(1-\frac{\beta}{15}\theta^2\right) \\
\implies \theta_1^2 &= \beta\theta^2\left[1+ 2c_k\theta^2\right] \label{eq:th1th-small}\\
\mathrm{where:~} c_k &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
A_k &\equiv \frac{1}{15}-\frac{3k}{20}
\end{align}

Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
expand each term as follows (neglecting terms of order four or higher):

\begin{align}
\theta_1 = &= \beta^{1/2}\theta\left[1+ 2c_k\theta^2\right]^{1/2} \\
\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2c_k\theta^2\right)\right]\\
\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
 &= \beta^{1/2}\theta\left[1+\left(c_k-\frac{1}{6}\beta\right)\theta^2\right] \\
 \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
 \right)^2}{6}\right] \\
 &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{c_k\beta^{1/2}}{1+\beta^{1/2}}
 -\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
\end{align}

So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:

\begin{align}
\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
\left\lbrace 1 + \theta^2\left[\frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
\right)\right] \right\rbrace \label{eq:r-small-theta}
\end{align}

Returning to equation (\ref{eq:R-exp}) we see the following:

\begin{align}
R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
\gamma &= \frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right) \label{eq:app-gamma}
\end{align}

We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
needed term to calculate the radius of curvature at the axis.

\section{Analytic derivation of $R_{90}$ in the Thin Shell model}
\label{app:r90-analytic}

To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
at $\theta=\frac{\pi}{2}$:

\begin{align}
R_{90} = D\tan\theta_{1,90} \\
\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
\end{align}
Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
the parameter $\xi\equiv \frac{2}{k+2}$ we have:
\begin{align}
R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
\end{align}

Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
becomes:

\begin{align}
\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
\end{align}
